%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Nikunj}{Goel}
\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{Department of Ecology and Evolutionary Biology, Yale University}{New Haven, Connecticut, 06511, USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(347)~679~9384}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{nikunj.goel@yale.edu}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Research Interest}

I am broadly interested in understanding distribution patterns of organisms across spatial and temporal scales. In my Ph.D., I am working at an intersection of mathematical models and empirical data to understand the role of seed dispersal in describing distribution patterns and resilience of tropical savanna and forest biomes.

\section{Education and Training}
\cventry{2015--present}{Ph.D.}{Yale University}{New Haven}{Department of Ecology and Evolutionary Biology, GPA:3.66/4}{}
\cventry{2011--2015}{Bachelor of Science (Research)}{Indian Institute of Science}{Bangalore}{GPA:6.25/8}{Physics major and Environmental Science minor}  % arguments 3 to 6 can be left empty

\section{Publications}
\begin{itemize}
\item{\textbf{Goel, N.}, Vleck, E. V \& Staver, A. C. Paleo evidence and spatial model do not support the island-wide forest claim in Madagascar, under preparation.}\\
\item{\textbf{Goel, N.}, Guttal, V., Levin, S. A, \& Staver, A. C. The role of dispersal in the maintenance of tropical savanna and its alternative biome state forest, under preparation.}\\
\item{Guttal, V.$^*$, Raghavendra, S.$^*$, \textbf{Goel, N.}$^*$, \& Hoarau, Q. (2016). Lack of critical slowing down suggests that financial meltdowns are not critical transitions, yet rising variability could signal systemic risk. PloS one, 11(1), e0144198..\\{\footnotesize $\ast$ All these authors contributed equally to the work. This article was covered by \href{http://www.natureasia.com/en/nindia/article/10.1038/nindia.2016.4}{\textit{Nature India}} and \href{http://www.deccanherald.com/content/523339/look-natural-disasters-prevent-big.html}{\textit{Deccan Herald}}.}}
\end{itemize}

\section{Teaching Experience}

\begin{itemize}
\item Plant Ecology (EEB 305) \hfill Spring 2018\\ 
{\footnotesize Teaching fellow at Department of Ecology and Evolutionary Biology, Yale University}\\

\item  Introduction to Statistics: Life Sciences (EEB 210) \hfill Spring 2017\\ 
{\footnotesize Teaching fellow at Department of Ecology and Evolutionary Biology, Yale University}\\

\item Ecology and Evolutionary Biology (BIOL 104) \hfill Spring 2016\\ 
{\footnotesize Teaching fellow at Department of Ecology and Evolutionary Biology, Yale University}\\

\end{itemize}


\section{Honors and Awards}
\begin{itemize}

\item Bunker Fellowship \hfill 2017-2018\\ 
{\footnotesize Department of Ecology and Evolutionary Biology, Yale University}\\

\item Ton Damman Award for best graduate student talk  \hfill 2016\\ 
{\footnotesize Vegetation section, Ecological Society of America}\\

\item Volterra Award for best graduate student talk \hfill 2016\\
{\footnotesize Theory Section, Ecological Society of America}\\

\item Poster presentation award  \hfill 2016 and 2017\\
{\footnotesize Annual Graduate Student Symposium at EEB, Yale University}\\

\item Awarded \emph{$1^{st}$} prize in \emph{Mathematics of Planet Earth} (MPE) competition, aimed at\\ promoting mathematical research on various natural processes\hfill 2013\\
{\footnotesize TIFR Centre For Applicable Mathematics, Bangalore}\\
\item  Kishore Vaigyanik Protsahan Yojana (KVPY) Fellowship \hfill 2011-2015\\
{\footnotesize National Science Fellowship, Department of Science and Technology, Government of India}\\
  
\end{itemize}

\section{Grants and Other Funding}
\begin{itemize}

\item RMSC Travel fund  \hfill 2017\\ 
{\footnotesize Department of Mathematics and Statistics, University of North Carolina at Greensboro}\\  

\item AISC Travel fund  \hfill 2016\\ 
{\footnotesize Department of Mathematics and Statistics, University of North Carolina at Greensboro}\\

\item Department Chair’s Fund \hfill 2016\\ 
{\footnotesize Department of Ecology and Evolutionary Biology, Yale University}\\
  
\end{itemize}

\section{Presentations}

\begin{itemize}

\item{\textbf{Goel, N.}, Guttal, V., Levin, S. A, \& Staver, A. C. The role of space in maintaining tropical savanna and its alternative biome state, forest. Paper presented at the Annual Regional Mathematics and Statistics Conference at University of North Carolina. Greensboro, NC. November 2017.}\\

\item{\textbf{Goel, N.}, Vleck, E. V \& Staver, A. C. The role of topographical barriers in maintaining savannas of Central Madagascar. Poster presented at the Yale EEB Department Annual Graduate Student Symposium. New Haven, CT. May 2017. \underline{\textbf{First Place}}}\\

\item{\textbf{Goel, N.}, Guttal, V., Levin, S. A, \& Staver, A. C. Spatial interactions increase the resilience of tropical biomes to global change. Paper presented at CES In-House Symposium. Bangalore, Karnataka August. 2016.}\\

\item{\textbf{Goel, N.}, Guttal, V.$^*$, Raghavendra, S.$^*$, \& Hoarau, Q. Early warning signals of financial meltdowns. Paper presented at International Conference on Advances in Interdisciplinary Statistics and Combinatorics at University of North Carolina. Greensboro, NC. September 2016.}\\

\item{\textbf{Goel, N.}, Guttal, V., Levin, S. A, \& Staver, A. C. Spatiotemporal dynamics of savanna and forest distribution. Paper presented at the Ecological Society of America Annual Meeting. Fort Lauderdale, FL. August 2016. \underline{\textbf{Volterra and Ton Damman Award}}}\\

\item{\textbf{Goel, N.}, Guttal, V., Levin, S. A, \& Staver, A. C. Spatiotemporal dynamics of savanna and forest distribution. Poster presented at the Yale EEB Department Annual Graduate Student Symposium. New Haven, CT. May 2016. \underline{\textbf{Second Place}}}\\

\end{itemize}

\section{\textsc{Relevant Courses Taken}}

\begin{itemize}
\setlength\itemsep{2.5pt}
\item Ecology  \\
a) Theoretical and Mathematical Ecology\\ {\footnotesize Discrete and continuous population models, random walks and diffusion, stochasticity in ecology and evolution, Hardy-Weinberg equilibrium, drift, game theory, Price equation, invasibility etc.} \\
b) Spatial Dynamics in Biology\\ {\footnotesize Linear stability analysis, reaction diffusion equations, stochastic differential equations, Fokker Planck equations, cellular automata models, mean field models, agent based models.}
\item Computational - Introduction to Algorithms and Scientific Computing 
\item Mathematics - Probability, Linear Algebra, Calculus,  Ordinary and Partial Differential Equations
\item Physics - Statistical Mechanics, Classical Mechanics, Mathematical Methods in Physics, Quantum Mechanics
\end{itemize}

\section{Science Outreach}
\begin{itemize}

% \item Rosenkranz Grants for Pedagogical Innovation \hfill [2017]\\
% {\footnotesize Contributor to an online library of short lectures on the leading edge of ecology and evolutionary biology for High School students.}

\item Participant in Flipped Science Fair (FSF) \hfill 2017\\
{\footnotesize FSF is a science outreach activity to inspire the next generation of scientists while training the scientists of today to effectively communicate their research to any audience.}\\

\item Organized an experimental physics event on Open Day\hfill 2013 and 2012\\
{\footnotesize Open Day is the occasion where the Indian Institute of Science opens its doors to general public to visit, learn, ask and understand the research-culture at IISc.}

\end{itemize}

% \section{Computer skills}
% \cvdoubleitem{Coding languages}{R, Matlab, C, C$++$}{}{}
% \cvdoubleitem{Typesetting}{\LaTeX, Microsoft Office}{}{}


\section{\textsc{References}}
\begin{itemize}
\setlength\itemsep{2.5pt}

\item \textbf{Dr. Carla A. Staver,} Department of Ecology and Evolutionary Biology, Yale University, New Haven, Connecticut, 06511, USA. Email: \emph{carla.staver@yale.edu} 

\item \textbf{Dr. Vishwesha Guttal,} Centre for Ecological Sciences, Indian Institute of Science, Bangalore, Karnataka, 560012, India. Email: \emph{guttal@ces.iisc.ernet.in}

\item \textbf{Dr. Stephen C. Stearns,} Department of Ecology and Evolutionary Biology, Yale University, New Haven, Connecticut, 06511, USA. Email: \emph{stephen.stearns@yale.edu} 
\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%\clearpage

%-----       letter       ---------------------------------------------------------
% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle

%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

%Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.

%Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.

%Albert Einstein discovered that $e=mc^2$ in 1905.

%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]

%\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
